Draft - sGBJ

### 2025-03-12 reporting/master_draft/draft_sgbj.qmd
update results with clean online data

```{r}
lsdata <- readRDS(file = here::here("data/breast_cancer/datamanaged.rds"))

load(here::here("data/breast_cancer/BreastCancer-Vijver-Clinical.RData"))

@@

```{r descbreast}
##### Description
df_data |> 
  dplyr::select(age,
                event,
                time,
                grade) |> 
  gtsummary::tbl_summary()

clin.data |> 
  mutate(event = factor(evmeta+evdeath>0,
                        levels = c(T,F),
                        labels = c("Yes", "No"))) |> 
  dplyr::select(Age = age,
                "Composite event" = event,
                "Follow-up" = tsurv,
                "Grade" = grade) |> 
    gtsummary::tbl_summary()

>>>>

```{r}
lsdata <- readRDS(file = here::here("data/breast_cancer/datamanaged2.rds"))

@@

```{r descbreast}
##### Description
df_data |> 
  dplyr::select(age,
                event,
                time_follow_up,
                grade) |> 
  gtsummary::tbl_summary()
